A Study on Penguins: A Minimal Reproducible Example

### 2024-08-22 01_Example/Manuscript.qmd
Add proper prefixes for table and figure

```{r}
#| label: "descriptive-statistics"
#| echo: false
#| results: "asis"

@@

```{r}
#| label: "bill-length-comparison"
#| echo: false
#| fig-cap: "Scatter Plot of Bill Lengths by Sex With Violin Plot Showing Quartiles"

>>>>

```{r}
#| label: "tbl-descriptive-statistics"
#| echo: false
#| results: "asis"

@@

```{r}
#| label: "fig-bill-length-comparison"
#| echo: false
#| fig-cap: "Scatter Plot of Bill Lengths by Sex With Violin Plot Showing Quartiles"
